### 2019-07-18 draft.tex
*** empty log message ***

On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and technically infinite energy source
when scientists and engineers manage to succeed at obtaining a controlled, and
energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
everyday life are rare, restricted to the occurrence of lightning during storms
and beautiful auroras that are spotted at high latitudes. In the interplanetary
and interstellar space, however, the situation is the opposite. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter is in the plasma state \cite{may}.

@@

>>>>

On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and technically infinite energy source
when scientists and engineers manage to succeed at obtaining a controlled, and
energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
everyday life are rare, restricted to the occurrence of lightning during storms,
flames and beautiful auroras that are spotted at high latitudes. In the
interplanetary and interstellar space, however, the situation is the opposite.
Starting in the outer layers of Earth's atmosphere, passing through the solar
wind in the interplanetary space, to the stellar interiors and atmospheres,
accretion disks, and molecular clouds it is estimated that something around
$99 \sim 99.9\%$ of the observable matter is in the plasma state \cite{may}.

@@

%The plasma that permeates the near Earth environment, and our solar system
% has its source in the plasma ejections

% During the development of this doctoral research, there was always a
% concern about not being restricted to purely theoretical modeling of
% the plasma phenomena.

% Describing nonlinear processes in plasmas, in
% the kinetic theory level, requires a series of approximations and
% idealized assumptions that, at first glance, it might look like one
% is losing the connection with the real-world physics.

% On Earth, the plasma is considered an exotic state of matter, associated to
% the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
% research laboratories, and the promise of cleaner and technically infinite
% energy source when scientists and engineers manage to succeed at obtaining
% a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
% Naturally occurring plasmas in our everyday life are rare, restricted to the
% occurrence of lightning during storms, flames, and the beautiful auroras that
% take place at high latitudes. In the interplanetary and interstellar space,
% however, the situation is the opposite. Starting in the outer layers of
% Earth's atmosphere, passing through the solar wind in the interplanetary space,
% to the stellar interiors and atmospheres, accretion disks, and molecular clouds
% it is estimated that something around $99 \sim 99.9\%$ of the observable matter
% in the universe is in the plasma state \cite{may}. Therefore, the study and
% comprehension of the physics of plasma processes is a fundamental branch of
% astrophysics.

% Plasma is a gas in which the atoms -or molecules- are in an ionized state.
% In such condition, long-range electric and magnetic forces determine the
% interactions of the charged particles. This coupling between the variations
% in the electric and magnetic fields and the motion of ions and electrons
% is behind the collective behavior that characterizes the plasma dynamics
% \cite{tsytotp}. The complex processes
